### 2021-05-09 papers/SYRCoSE/regmachine-eventstruct.tex
minor clarification
commas? (this looks better but still feels a bit weird)

Let us consider an example. Given the program below, 
our semantics builds the event structure as 
shown in \cref{fig:regmachine-eventstruct-example}.

@@

The construction starts from an initial event structure,
containing for each thread an event labelled by $\tslab{}$.
We depict the corresponding thread state below the label.
Initially, each event is mapped to an initial thread state
consisting of an instruction pointer pointing to the first 
instruction to be executed and an initial mapping of registers
denoted as $\bot$.
The first step executes the store instruction from 
the leftmost thread and exits the program, 
since the execution of this thread terminates
(we omit the $\exitInst$ instructions at the end of each thread for brevity).
Next, the store from the rightmost thread is executed and corresponding
write event gets added to the structure. 
After that the load instruction from the middle thread is executed. 
Since there are two matching write events in the event structure, 
two conflicting reads are conjoined to the event structure. 
Note that the events can be added non-deterministically in any order
respecting causality. We could have first executed the rightmost thread
and added write $\wlab{x}{2}$ before $\wlab{x}{1}$, 
or we could have added the read with label $\rlab{x}{2}$ 
before another read $\rlab{x}{1}$.

>>>>

Let us consider an example. Given the program below, 
our semantics builds the corresponding event structure as 
shown in \cref{fig:regmachine-eventstruct-example}.

@@

The construction starts from an initial event structure
containing, for each thread, an event labelled by $\tslab{}$.
We depict the corresponding thread state below the label.
Initially, each event is mapped to an initial thread state
consisting of an instruction pointer pointing to the first 
instruction to be executed and an initial mapping of registers
denoted as $\bot$.
The first step executes the store instruction from 
the leftmost thread and exits the program, 
since the execution of this thread terminates
(we omit the $\exitInst$ instructions at the end of each thread for brevity).
Next, the store from the rightmost thread is executed and corresponding
write event gets added to the structure. 
After that the load instruction from the middle thread is executed. 
Since there are two matching write events in the event structure, 
two conflicting reads are conjoined to the event structure. 
Note that the events can be added non-deterministically in any order
respecting causality. We could have first executed the rightmost thread
and added write $\wlab{x}{2}$ before $\wlab{x}{1}$, 
or we could have added the read with label $\rlab{x}{2}$ 
before another read $\rlab{x}{1}$.
